Transfer Learning for Depression Detection on Social Networks\thanks{Supported by School of Information System, University of Southern Queensland, Australia}

### 2018-11-04 Paper/version 0/paper.tex
close to version 1

Zimmerman et, al. [Zimmerman] compared a preferred scale measure "IDD" of depression to psychiatric interview and found that it had good reliability and was significantly associated with the result of clinician's diagnosis. The proposed method had a 97.2 \% [Zimmerman] overall accuracy on the criterion of clinic diagnosis. And new method is suggested to be an inexpensive way to collect large homogeneous cases to screen depression. However, the research also appointed three apparent reasons why self-report depression scales generally performed poorer than psychiatric interview: first, scale measure covered less diagnostic criteria for major depressive disorder than interviews; second, non-criteria items in depression scale inventory decreased specificity of performance; and self-report scales did not assess symptom duration and exclusion criteria which may reverse the previous judgement [[Zimmerman]]. The classification via scale measure and clinical interview implied contrasting algorithms [Zimmerman] to screen depression but all based on the depression diagnostic criteria.

@@

Kroenke et, al. [PHQ-9] discovered that there was a strong association between increasing depression severity screen scores and worsening functionality on all 6 variables: mental, social, role, pain, physical and general functions. The research illustrated graphically the relationship between increasing PHQ-9 scores of depression and worsening functional variables (see Fig.~\ref{fig2}). 

@@

By analysis of the relationship between depression and variables of functional status, the scales of health-related functional variables have the similar trend as the severity of depression in statistics. Previous studies in related-work were more focused on detecting depressive symptoms and depression-related contents. Likewise, this relationship innovates a new potential method of predicting users' depression by sampling various health-related functional conditions. The classification technique and binary ground truth technique will enhance the strength of new type prediction as well. New method apparently has a couple benefits comparing to previous techniques:
\begin{enumerate}[label=\alph*)]
  \item There are more features available for classification due to enlarged inputs in various functional areas;
  \item It is more easier to acquire functional data than sensitive data of depressive symptoms especially on social network; 
  \item It is more easier to cover sufficient specificities of one functional status than to cover all available types of depressive symptoms;
  \item It is more accuracy and more comparable in the classification of six functional status group than in only one collection of depressive symptoms;
  \item It can provide a real opportunity to apply the similar method on automatically detecting depression on social network.
\end{enumerate}

Therefore, we can transfer psychological domain knowledge to information domain. \textit{$|\mathbb{D}^s|$} can be narrowed down to 6. The dataset of user mental profile need to be redefined:\\
\\
\textbf{Definition 4} Let new redesigned $\mathbb{U}$ = $\langle u_{mental}, u_{social}, u_{role}, u_{pain}, u_{physical}, u_{general} \rangle$, every u  $\in \mathbb{U}$ is an independent function of user, where
\begin{itemize}
  \item $u_{mental}$ presents mental functional variables;
  \item $u_{social}$ presents social functional variables;
  \item $u_{role}$ presents role functional variables;
  \item $u_{pain}$ presents pain functional variables;
  \item $u_{physical}$ presents physical functional variables;
  \item $u_{general}$ presents the overall functional variables.
\end{itemize}
%
%
\subsection{Data Processing}
%
\paragraph{}
In this research, we use the dataset that was directly collected from national health examination survey. It is generally used for health statistics, but unfortunately not for data mining. And we only use the survey question part which was one third of whole dataset. It was organised by variety of health survey questions which divided questions into columns and participants into rows amongst different tables of health domain. Since those tables were not organised in the same format and structure, the pre-processing of them is hence prominent for later classification.

Data cleaning and transformation is prior in the whole procedure of data preparation because all data should be computer readable and not redundant. And data types in the dataset are justified in order to make each other compatible and comparative. The normalisation is also necessary to uniform the scale condition in various questions. Whilst data preprocessing is implemented, psychological domain knowledge in functionality classes is applied in the reconstruction of data structure. According to Definition 4, we can lower the dimension of data set by reducing the number of tables. All tables need to be reconstructed into only six tables referred by six classes of health functionings (see Fig.~\ref{fig3}).
\begin{figure}[h]
\includegraphics[width=1\textwidth]{restructure.png}
\caption{Data Restructure based on Psychological Knowledge Base} \label{fig3}
\end{figure}
They may involve different number of questions but they all have the same participants. Furthermore, those six tables can be rejoin into one big table due to same row index of them. By instant consideration of those tables, each table forms a new dataset where participants are cases and questions are features. We can therefore define the new datasets after data pre-processing as below:\\
\\
\textbf{Definition 5} Let new overall dataset of m cases and n features $\mathbb{D}_{overall}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$, and sub-datasets of different 6 functionings $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{role}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{physical}$ and $\mathbb{D}_{general}$, where
\begin{itemize}
  \item $|\mathbb{D}_{overall}|$ = $|\mathbb{D}_{mental}|$ = $|\mathbb{D}_{social}|$ = $|\mathbb{D}_{role}|$ = $|\mathbb{D}_{pain}|$ = $|\mathbb{D}_{physical}|$ = $|\mathbb{D}_{general}|$ = $m$;
  \item Feature($\mathbb{D}_{mental}$) + Feature($\mathbb{D}_{social}$) + Feature($\mathbb{D}_{role}$) + Feature($\mathbb{D}_{pain}$) + Feature($\mathbb{D}_{physical}$) + Feature($\mathbb{D}_{general}$) = Feature($\mathbb{D}_{overall}$) = n .
\end{itemize}
%
%
\subsection{Modelling}
%
\paragraph{}
In this study, we use an ensemble classification approach to build the model for detecting depression. It implements the independent ensemble methodology which applies several classification techniques in parallel. They are Support Vector Machine (SVM) technique, Artificial Neutral Network(ANN) algorithm, K-Nearest Neighbour (KNN) method and Decision Tree (DT) method. Each composite classifier among them is trained on the same portion of the training set in one run. The performance of them are evaluated by k-fold cross validation algorithm. And amalgamating all outputs of composite classifiers into a single prediction, we consequently generates the ensemble classifier. The main idea of this ensemble classification approach is to collect various outputs of multiple independent classifiers and combines them to improve the predictive performance.

@@

By comparing the performances of four base models, Decision tree algorithm has the highest accuracy and F1 measure. SVM technique has a similar performance as decision tree algorithm but only a bit lagging in precision. ANN method performs more advantageous in precision score and KNN method operates more fitting in recall measurement. 

@@

\textbf{SVM}  & 0.921  & 0.927 & 0.990  & 0.958  \\ \hline

@@

\textbf{ANN} & 0.905 & 0.941 & 0.955 & 0.948 \\ \hline

@@

\textbf{KNN}  & 0.908   & 0.913  & 0.993  & 0.951  \\ \hline

@@

\textbf{DT} & 0.925  & 0.938 & 0.981  & 0.959  \\ \hline

@@

\textbf{ANN} & 0.948  & 0.052   & 0.283    \\ \hline

@@

@@

\textbf{$\mathbb{D}_{overall}$}& 98  & 0.976  & 0.954 \\ \hline

@@

\textbf{$\mathbb{D}_{mental}$ }  & 4  & 0.975  & 0.953  \\ \hline

@@

The F1 score is a weighted harmonic mean of precision and recall such that the best score is 1.0 and the worst is 0.0. F1 measure equally considers both precision and recall in the performance measurement.

@@

\textbf{SVM} & 0.9577  & 0.9498 & 0.9498  & 0.9498  & 0.9570  & 0.9498 & 0.9508 \\ \hline

@@

\textbf{ANN} & 0.9480  & 0.9435  & 0.9350  & 0.9421 & 0.9613 & 0.9498 & 0.9302 \\ \hline

@@

\textbf{KNN} & 0.9513  & 0.9468 & 0.9449 & 0.9438 & 0.9582 & 0.9382 & 0.9491 \\ \hline

@@

\textbf{DT} & 0.9591 & 0.9495  & 0.9492 & 0.9498  & 0.9601  & 0.9498 & 0.9501  \\ \hline

@@

\textbf{Ensemble}  & 0.9757  & 0.9637  & 0.9630  & 0.9639 & 0.9750 & 0.9610 & 0.9638  \\ \hline

@@

\textbf{SVM} & 0.9209  &0.9044 & 0.9044 & 0.9044 & 0.9192 & 0.9044  & 0.9065  \\ \hline

@@

\textbf{ANN} & 0.9053 & 0.8950 & 0.8793 & 0.8924 & 0.9283 & 0.9044 & 0.8729 \\ \hline

@@

\textbf{KNN} & 0.9080  & 0.9003 & 0.8960 & 0.8949 & 0.9228 & 0.8862 & 0.9036 \\ \hline

@@

\textbf{DT} & 0.9244 & 0.9046 & 0.9035  & 0.9051 & 0.9262 & 0.9044 & 0.9059 \\ \hline

@@

\textbf{Ensemble} & 0.9537 & 0.9306 & 0.9287  & 0.9306  & 0.9527 & 0.9249 & 0.9305  \\ \hline

@@

\textbf{SVM} & 0.9272 & 0.9044 & 0.9044  & 0.9044  & 0.9214  & 0.9044  & 0.9071  \\ \hline

@@

\textbf{ANN}   & 0.9413   & 0.9186   & 0.9107  & 0.9168   & 0.9385 & 0.9044 & 0.9239 \\ \hline

@@

\textbf{KNN} & 0.9127 & 0.9148 & 0.9071  & 0.9129 & 0.9379 & 0.9127  & 0.9083  \\ \hline

@@

\textbf{DT} & 0.9380  & 0.9103  & 0.9057  & 0.9104  & 0.9392 & 0.9044  & 0.9121   \\ \hline

@@

\textbf{Ensemble} & 0.9562  & 0.9335  & 0.9286 & 0.9306  & 0.9595  & 0.9249 & 0.9302 \\ \hline

@@

@@

\textbf{SVM} & 0.9904 & 1.0000  & 1.0000  & 1.0000  & 0.9956   & 1.0000   & 0.9989    \\ \hline

@@

\textbf{ANN}   & 0.9549 & 0.9700  & 0.9607  & 0.9690  & 0.9853  & 1.0000  & 0.9367     \\ \hline

@@

\textbf{KNN}  & 0.9934 & 0.9811  & 0.9860  & 0.9769 & 0.9795 & 0.9676  & 0.9937       \\ \hline

@@

\textbf{DT}  & 0.9814  & 0.9923  & 0.9972  & 0.9928 & 0.9821  & 1.0000  & 0.9916     \\ \hline

@@

\textbf{Ensemble}   & 1.0000 & 1.0000 & 1.0000  & 1.0000  & 0.9990  & 1.0000 & 1.0000   \\ \hline

@@

Ensemble classifier is obviously superior than baseline models as performing advantageous at all measures
in all datasets. 
\subsection{Discussions}
\section{Sensitivity Study}
SVM: 
A low C makes the decision surface smooth, while a high C aims at classifying all training examples correctly.
The larger gamma is, the closer other examples must be to be affected.
Proper choice of C and gamma is critical to the SVM’s performance. One is advised to use C and gamma spaced exponentially far apart to choose good values.

@@

\bibitem{ref_article}Andrea, S.B., Siegel, S.A.R., and Teo, A.R.: ‘Social Support and Health Service Use in Depressed Adults: Findings From the National Health and Nutrition Examination Survey’, General Hospital Psychiatry, 2016, 39, pp. 73-79
\bibitem{ref_article}Choudhary, R., and Gianey, H.K.: ‘Comprehensive Review On Supervised Machine Learning Algorithms’, in Editor (Ed.)\^(Eds.): ‘Book Comprehensive Review On Supervised Machine Learning Algorithms’ (2017, edn.), pp. 37-43
\bibitem{ref_article}Clark, M.M., Bradley, K.L., Jenkins, S.M., Mettler, E.A., Larson, B.G., Preston, H.R., Liesinger, J.T., Werneburg, B.L., Hagen, P.T., Harris, A.M., Riley, B.A., Olsen, K.D., and Vickers Douglas, K.S.: ‘The Effectiveness of Wellness Coaching for Improving Quality of Life’, Mayo Clinic Proceedings, 2014, 89, (11), pp. 1537-1544
\bibitem{ref_article}Fei, Y., and Li, W.-q.: ‘Improve artificial neural network for medical analysis, diagnosis and prediction’, Journal of Critical Care, 2017, 40, pp. 293
\bibitem{ref_article}Gonzalez-Saenz de Tejada, M., Bilbao, A., Baré, M., Briones, E., Sarasqueta, C., Quintana, J.M., Escobar, A., and Baré, M.: ‘Association of social support, functional status, and psychological variables with changes in health-related quality of life outcomes in patients with colorectal cancer’, Psycho-Oncology, 2016, 25, (8), pp. 891-897
\bibitem{ref_article}Kotsiantis, S.B., Zaharakis, I.D., and Pintelas, P.E.: ‘Machine learning: a review of classification and combining techniques’, Artificial Intelligence Review, 2006, 26, (3), pp. 159-190
\bibitem{ref_article}Kroenke, K., Spitzer, R.L., and Williams, J.B.: ‘The PHQ-9: validity of a brief depression severity measure’, J Gen Intern Med, 2001, 16, (9), pp. 606-613
\bibitem{ref_article}Kumar, R.: ‘Fundamental of artificial neural network and fuzzy logic’ (University Science Press, An Imprint of Laxmi Publications Pvt. Ltd., 2010. 2010)
\bibitem{ref_article}Limsetto, N., and Waiyamai, K.: ‘Handling Concept Drift via Ensemble and Class Distribution Estimation Technique’, in Editor (Ed.)\^(Eds.): ‘Book Handling Concept Drift via Ensemble and Class Distribution Estimation Technique’ (Springer Berlin Heidelberg, 2011, edn.), pp. 13-26
\bibitem{ref_article}Lu, Y., Cheung, Y.M., and Tang, Y.Y.: ‘Hybrid sampling with bagging for class imbalance learning’, in Editor (Ed.)\^(Eds.): ‘Book Hybrid sampling with bagging for class imbalance learning’ (Springer Verlag, 2016, edn.), pp. 14-26
\bibitem{ref_article}Merikangas, A., Mendola, P., Pastor, P., Reuben, C., and Cleary, S.: ‘The association between major depressive disorder and obesity in US adolescents: results from the 2001–2004 National Health and Nutrition Examination Survey’, Journal of Behavioral Medicine, 2012, 35, (2), pp. 149-154
\bibitem{ref_article}Nguyen, B., Weiss, P., Beydoun, H., and Kancherla, V.: ‘Association between blood folate concentrations and depression in reproductive aged U.S. women, NHANES (2011–2012)’, Journal of Affective Disorders, 2017, 223, pp. 209-217
\bibitem{ref_article}Ostir, G.V., Berges, I.M., Ottenbacher, A., and Ottenbacher, K.J.: ‘Patterns of change in depression after stroke’, J Am Geriatr Soc, 2011, 59, (2), pp. 314-320
\bibitem{ref_article}Rokach, L.: ‘Ensemble-based classifiers’, Artificial Intelligence Review, 2010, 33, (1), pp. 1-39
\bibitem{ref_article}Sagi, O., and Rokach, L.: ‘Ensemble learning: A survey’, Wiley Interdisciplinary Reviews: Data Mining and Knowledge Discovery, 2018, 8, (4), pp. e1249
\bibitem{ref_article}Serpen, G., and Pathical, S.: ‘Classification in High-Dimensional Feature Spaces: Random Subsample Ensemble’, in Editor (Ed.)\^(Eds.): ‘Book Classification in High-Dimensional Feature Spaces: Random Subsample Ensemble’ (2009, edn.), pp. 740-745
\bibitem{ref_article}Somvanshi, M., and Chavan, P.: ‘A review of machine learning techniques using decision tree and support vector machine’, in Editor (Ed.)\^(Eds.): ‘Book A review of machine learning techniques using decision tree and support vector machine’ (2016, edn.), pp. 1-7
\bibitem{ref_article}Tedders, S.H., Fokong, K.D., McKenzie, L.E., Wesley, C., Yu, L., and Zhang, J.: ‘Low cholesterol is associated with depression among US household population’, Journal of Affective Disorders, 2011, 135, (1-3), pp. 115-121
\bibitem{ref_article}Ubani, C.C., and Zhang, J.: ‘The role of adiposity in the relationship between serum leptin and severe major depressive episode’, Psychiatry Research, 2015, 228, (3), pp. 866-870
\end{thebibliography}
\end{document}

>>>>

Zimmerman et, al. [Zimmerman] compared a preferred scale measure "IDD" of depression to psychiatric interview and found that it had good reliability and was significantly associated with the result of clinician's diagnosis. The proposed method had a 97.2 \% [Zimmerman] overall accuracy on the criterion of clinic diagnosis. And new method is suggested to be an inexpensive way to collect large homogeneous cases to screen depression. However, the research also appointed three apparent reasons why self-report depression scales generally performed poorer than psychiatric interview: first, scale measure covered less diagnostic criteria for major depressive disorder than interviews; second, non-criteria items in depression scale inventory decreased specificity of performance; and self-report scales did not assess symptom duration and exclusion criteria which may reverse the previous judgement [Zimmerman]. The classification via scale measure and clinical interview implied contrasting algorithms [Zimmerman] to screen depression but all based on the depression diagnostic criteria.

@@

Kroenke et, al. [PHQ-9] discovered that there was a strong association between increasing depression severity screen scores and worsening functionality on all 6 categories: mental, social, role, pain, physical and general functions. These 6 categories were directly interpreted 5 items of mental health diagnostic criteria in Mental Health Inventory (MHI-5) and additionally mental disorder symptoms as mental category. The research illustrated graphically the relationship between increasing PHQ-9 scores of depression and worsening functional categories (see Fig.~\ref{fig2}). 

@@

By analysis of the relationship between depression and variables of functional status, the scales of health-related functional variables have the similar trend as the severity of depression in statistics. Previous studies in related-work were more focused on detecting depressive symptoms and depression-related contents. Likewise, this relationship innovates a new potential method of predicting users' depression by sampling various diagnostic criteria of functionality. The classification technique and binary ground truth technique will enhance the strength of new type prediction as well. New method apparently has a couple benefits comparing to previous techniques:
\begin{enumerate}[label=\alph*)]
  \item There are more features available for classification due to enlarged inputs in various functional areas;
  \item It is more easier to acquire functional data than sensitive data of depressive symptoms especially on social network; 
  \item It is more easier to cover sufficient specificities of one functional status than to cover all available types of depressive symptoms;
  \item It is more accuracy and more comparable in the classification of six functional status group than in only one collection of depressive symptoms;
  \item It can provide a real opportunity to apply the similar method on automatically detecting depression on social network.
\end{enumerate}

Therefore, we can transfer psychological domain knowledge to information domain. \textit{$\mathbb{D}^s$} can be leveraged and divide into 6 sub-datasets. The dataset of user mental profile need to be redefined:\\
\\
\textbf{Definition 4} Let new redesigned $\mathbb{U}$ = $\langle u_{mental}, u_{social}, u_{role}, u_{pain}, u_{physical}, u_{general} \rangle$, every u  $\in \mathbb{U}$ is an independent function of user, where
\begin{itemize}
  \item $u_{mental}$ presents individual mental disorder symptoms;
  \item $u_{social}$ presents mental diagnostic criteria in the social activities;
  \item $u_{role}$ presents mental diagnostic criteria in the role funcitonlity;
  \item $u_{pain}$ presents mental diagnostic criteria in the pain domain ;
  \item $u_{physical}$ presents mental diagnostic criteria in the physical category;
  \item $u_{general}$ presents mental diagnostic criteria in the general actions.
\end{itemize}
%
%
\subsection{Data Processing}
%
\paragraph{}
In this research, we use the dataset that was directly collected from national health examination survey. It is generally used for health statistics, but unfortunately not for data mining. And we only use the survey question part which was one third of whole dataset. It was organised by variety of health survey questions which divided questions into columns and participants into rows amongst different tables of health domain. Since those tables were not organised in the same format and structure, the pre-processing of them is hence prominent for later classification.

Data cleaning and transformation is prior in the whole procedure of data preparation because all data should be computer readable and not redundant. And data types in the dataset are justified in order to make each other compatible and comparative. The normalisation is also necessary to uniform the scale condition in various questions. Whilst data preprocessing is implemented, psychological domain knowledge in functional diagnostic criteria is applied in the reconstruction of data structure. According to Definition 4, we can lower the dimension of data set by reducing the number of tables. All tables need to be reconstructed into only six tables referred by six categories of depression diagnostic criteria in functionality (see Fig.~\ref{fig3}).
\begin{figure}[h]
\includegraphics[width=1\textwidth]{restructure.png}
\caption{Data Restructure based on Psychological Knowledge Base} \label{fig3}
\end{figure}
They may involve different number of questions but they all have the same participants. Furthermore, those six tables can be rejoin into one big table due to same row index of them. By instant consideration of those tables, each table forms a new dataset where participants are cases and questions are features. We can therefore define the new datasets after data pre-processing as below:\\
\\
\textbf{Definition 5} Let new overall dataset of m cases and n features $\mathbb{D}_{overall}$ = $\displaystyle \big\{ (x_{1}, x_{2}, ... , x_{n}, y ), x_{i} \in R^{m}, y \in {\{0, 1\}}^{m}  \big\}$, and sub-datasets of different 6 functional categories $\mathbb{D}_{mental}$, $\mathbb{D}_{social}$, $\mathbb{D}_{role}$, $\mathbb{D}_{pain}$, $\mathbb{D}_{physical}$ and $\mathbb{D}_{general}$, where
\begin{itemize}
  \item $|\mathbb{D}_{overall}|$ = $|\mathbb{D}_{mental}|$ = $|\mathbb{D}_{social}|$ = $|\mathbb{D}_{role}|$ = $|\mathbb{D}_{pain}|$ = $|\mathbb{D}_{physical}|$ = $|\mathbb{D}_{general}|$ = $m$;
  \item Feature($\mathbb{D}_{mental}$) + Feature($\mathbb{D}_{social}$) + Feature($\mathbb{D}_{role}$) + Feature($\mathbb{D}_{pain}$) + Feature($\mathbb{D}_{physical}$) + Feature($\mathbb{D}_{general}$) = Feature($\mathbb{D}_{overall}$) = n .
\end{itemize}
%
%
\subsection{Modelling}
%
\paragraph{}
In this study, we use an ensemble classification approach to build the model for detecting depression. It implements the independent ensemble methodology which applies several classification techniques in parallel. They are Support Vector Machine (SVM) technique, Artificial Neutral Network(ANN) algorithm, K-Nearest Neighbour (KNN) method and Decision Tree (DT) method. Each composite classifier among them is trained on the same portion of the training set in one run. The performance of them are evaluated by k-fold cross validation algorithm. And amalgamating all outputs of composite classifiers into a single prediction, we consequently generates the ensemble classifier. The main idea of this ensemble classification approach is to collect various outputs of multiple independent classifiers and combines them to improve the predictive performance.

@@

By comparing the performances of four base models (illustrated in table. 1), Decision tree algorithm has the highest accuracy and F1 measure. SVM technique has a similar performance as decision tree algorithm but only a bit lagging in precision. ANN method performs more advantageous in precision score and KNN method operates more fitting in recall measure. Almost F1 scores and recall measures are significant in correlation ( $\geq$ 95\%). However, baseline models perform less satisfied in accuracy and precision. 

@@

\textbf{SVM}  & 0.921  & 0.927 & 0.990  & \textbf{0.958}  \\ \hline

@@

\textbf{ANN} & 0.905 & \textbf{0.941} & 0.955 & 0.948 \\ \hline

@@

\textbf{KNN}  & 0.908   & 0.913  & \textbf{0.993}  & 0.951  \\ \hline

@@

\textbf{DT} & \textbf{0.925}  & 0.938 & 0.981  & \textbf{0.959}  \\ \hline

@@

\textbf{ANN} & 0.948  & 0.052   & \textbf{0.283}    \\ \hline

@@

We use F1 score and accuracy measure as the main predication indicators of the ensemble classification. As features and specificity of the overall dataset and each sub-datasets varied, the divided performances are expected (see table. 3). Unsurprisingly, ensemble classifier performs better in the overall dataset and mental sub-set. Performances in other sub-sets is compromised in this experiment but is still comparable to other machine learning methodologies [Fatima][Hassan][Peng][Reece]. As DT performs best (0.925 in Accuracy) in the sub-models and ensemble model has a overall Accuracy of 0.954, the improvement $I$ for detecting depression in ensemble classifier is calculated as below (let percentage of depressed instances as $N_{0}$):\\
\begin{equation}\label{reio}
	 I = \frac{Accuracy_{new} - Accuracy_{old}}{N_{0}} = \frac{0.954 - 0.925}{9.56\%} \cdot 100\% = 30.3\%
\end{equation}
Therefore, the proposed ensemble approach increases the predictive performance by 30.3\% for distinguishing depression from non-depressed participants.

@@

\textbf{$\mathbb{D}_{overall}$}& 98  & \textbf{0.976}  & \textbf{0.954} \\ \hline

@@

\textbf{$\mathbb{D}_{mental}$ }  & 4  & \textbf{0.975}  & \textbf{0.953}  \\ \hline

@@

F1 score is a weighted harmonic mean of precision and recall such that the best score is 1.0 and the worst is 0.0. F1 measure equally considers both precision and recall in the performance measurement. By the comparison of F1 measures in both different algorithms and datasets (see table. 4), ensemble method has a better F1 score than other baseline algorithms. The overall dataset and mental subset enable to be distinguished from other datasets due to a higher level of F1 measures.

@@

\textbf{SVM} & 0.9577  & 0.950 & 0.950  & 0.950  & 0.957  & 0.950 & 0.951 \\ \hline

@@

\textbf{ANN} & 0.948  & 0.944  & 0.935  & 0.942 & 0.961 & 0.950 & 0.930 \\ \hline

@@

\textbf{KNN} & 0.951  & 0.947 & 0.945 & 0.944 & 0.958 & 0.938 & 0.949 \\ \hline

@@

\textbf{DT} & 0.959 & 0.950  & 0.949 & 0.950  & 0.960  & 0.950 & 0.950  \\ \hline

@@

\textbf{Ensemble}  & \textbf{0.976}  & 0.964  & 0.963  & 0.964 & \textbf{0.975} & 0.961 & 0.964  \\ \hline

@@

\textbf{SVM} & 0.921  &0.904 & 0.904 & 0.904 & 0.919 & 0.904  & 0.907  \\ \hline

@@

\textbf{ANN} & 0.905 & 0.895 & 0.879 & 0.892 & 0.928 & 0.904 & 0.873 \\ \hline

@@

\textbf{KNN} & 0.908  & 0.900 & 0.896 & 0.895 & 0.923 & 0.886 & 0.904 \\ \hline

@@

\textbf{DT} & 0.924 & 0.905 & 0.904  & 0.905 & 0.926 & 0.904 & 0.906 \\ \hline

@@

\textbf{Ensemble} & \textbf{0.954} & 0.931 & 0.929  & 0.931  & 0.953 & 0.925 & 0.931  \\ \hline

@@

\textbf{SVM} & 0.927 & 0.904 & 0.904  & 0.904  & 0.921  & 0.904  & 0.907  \\ \hline

@@

\textbf{ANN}   & 0.941   & 0.919   & 0.911  & 0.917   & 0.939 & 0.904 & 0.924 \\ \hline

@@

\textbf{KNN} & 0.913 & 0.915 & 0.907  & 0.913 & 0.938 & 0.913  & 0.908  \\ \hline

@@

\textbf{DT} & 0.938  & 0.910  & 0.906   & 0.910  & 0.939 & 0.904  & 0.912   \\ \hline

@@

\textbf{Ensemble} & 0.956  & 0.934  & 0.929 & 0.931  & \textbf{0.960}  & 0.925 & 0.930 \\ \hline

@@

For the performances of precision, ensemble classifier has the best precision in each dataset and it surprisedly performs better in metal sub-dataset than in the overall dataset. It may approve that features for metal disorder symptoms is more depression-related than other features in other categories because non-criteria items in depression scale decreased specificity of performance [Zimmerman].

@@

\textbf{SVM} & 0.990 & 1.000  & 1.000  & 1.000  & 0.996   & 1.000   & 0.999    \\ \hline

@@

\textbf{ANN}   & 0.955 & 0.970  & 0.961  & 0.969  & 0.985  & 1.000  & 0.937     \\ \hline

@@

\textbf{KNN}  & 0.993 & 0.981  & 0.986  & 0.977 & 0.980 & 0.968  & 0.994      \\ \hline

@@

\textbf{DT}  & 0.9814 & 0.992  & 0.997  & 0.993 & 0.982  & 1.000  & 0.992    \\ \hline

@@

\textbf{Ensemble}   & \textbf{1.000} & 1.000 & 1.000  & 1.000  & 0.999  & 1.000 & 1.000   \\ \hline

@@

The recall performances of ensemble classifier is about 1 in the overall dataset and all sub-datasets. According to the definition of recall measure  $ Recall = \frac{TP}{TP + FN} $, it means that only when false negative measurement (FN) is 0, recall measure is equal to 1. In our experiment, FN presents the number of depressed users who were incorrectly identified as non-depressed. As FN is zero, it indicates that no depressed instances in the experiment has been mistakenly classified. The coverage in correct classification of depressed participants is perfect, only slightly larger than the results of psychological screening ( illustrated in Fig.~\ref{fig5} ). Let the predicted precision as $Precision_{p}$ and percentage of non-depressed instances as $N_{1}$, the overall prediction $p_{overall}$of depressed instances is calculated as below:\\
	p_{overall} = 1 - (Precision_{p} \cdot N_{1})= (1 -  0.956 \cdot 90.44\%) \cdot 100\% = 13.54\%

\begin{figure}[h]
\includegraphics[width=1\textwidth]{coverage.png}
\caption{Coverage in correct classification of depression} \label{fig5}
\end{figure}
%
%
%
%
%
%
\subsection{Discussions}
\paragraph{performance of ensemble is great}
Ensemble classifier is obviously superior than baseline models as performing advantageous at both all measures and experiment. 
%
%
\paragraph{the coverage of depression is greate}
%
%
%
%
%
\paragraph{enlarge the area for collecting data, more features}
%
%
%
%
%
%
%
%
%
%
%
%
%
%
\pagebreak
\section{Sensitivity Study}
%
%
%
SVM: 
A low C makes the decision surface smooth, while a high C aims at classifying all training examples correctly.
The larger gamma is, the closer other examples must be to be affected.
Proper choice of C and gamma is critical to the SVM’s performance. One is advised to use C and gamma spaced exponentially far apart to choose good values.

@@

1	Andrea, S.B., Siegel, S.A.R., and Teo, A.R.: ‘Social Support and Health Service Use in Depressed Adults: Findings From the National Health and Nutrition Examination Survey’, General Hospital Psychiatry, 2016, 39, pp. 73-79
\\\\
2	Choudhary, R., and Gianey, H.K.: ‘Comprehensive Review On Supervised Machine Learning Algorithms’, in Editor (Ed.)\^(Eds.): ‘Book Comprehensive Review On Supervised Machine Learning Algorithms’ (2017, edn.), pp. 37-43
\\\\
3	Clark, M.M., Bradley, K.L., Jenkins, S.M., Mettler, E.A., Larson, B.G., Preston, H.R., Liesinger, J.T., Werneburg, B.L., Hagen, P.T., Harris, A.M., Riley, B.A., Olsen, K.D., and Vickers Douglas, K.S.: ‘The Effectiveness of Wellness Coaching for Improving Quality of Life’, Mayo Clinic Proceedings, 2014, 89, (11), pp. 1537-1544
\\\\
4	De Choudhury, M., Counts, S., and Horvitz, E.: ‘Social media as a measurement tool of depression in populations’, 2013, pp. 47-56
\\\\
5	Fatima, I., Mukhtar, H., Ahmad, H.F., and Rajpoot, K.: ‘Analysis of user-generated content from online social communities to characterise and predict depression degree’, Journal of Information Science, 2018, 44, (5), pp. 683-695
\\\\
6	Fei, Y., and Li, W.-q.: ‘Improve artificial neural network for medical analysis, diagnosis and prediction’, Journal of Critical Care, 2017, 40, pp. 293
\\\\
7	Gonzalez-Saenz de Tejada, M., Bilbao, A., Baré, M., Briones, E., Sarasqueta, C., Quintana, J.M., Escobar, A., and Baré, M.: ‘Association of social support, functional status, and psychological variables with changes in health-related quality of life outcomes in patients with colorectal cancer’, Psycho-Oncology, 2016, 25, (8), pp. 891-897
\\\\
8	Hassan, A.U., Hussain, J., Hussain, M., Sadiq, M., and Lee, S.: ‘Sentiment analysis of social networking sites (SNS) data using machine learning approach for the measurement of depression’, in Editor (Ed.)\^(Eds.): ‘Book Sentiment analysis of social networking sites (SNS) data using machine learning approach for the measurement of depression’ (IEEE, 2017, edn.), pp. 138-140
\\\\
9	Huerta-Ramírez, R., Bertsch, J., Cabello, M., Roca, M., Haro, J.M., and Ayuso-Mateos, J.L.: ‘Diagnosis delay in first episodes of major depression: A study of primary care patients in Spain’, Journal of Affective Disorders, 2013, 150, (3), pp. 1247-1250
\\\\
10	Kotsiantis, S.B., Zaharakis, I.D., and Pintelas, P.E.: ‘Machine learning: a review of classification and combining techniques’, Artificial Intelligence Review, 2006, 26, (3), pp. 159-190
\\\\
11	Kroenke, K., Spitzer, R.L., and Williams, J.B.: ‘The PHQ-9: validity of a brief depression severity measure’, J Gen Intern Med, 2001, 16, (9), pp. 606-613
\\\\
12	Kumar, R.: ‘Fundamental of artificial neural network and fuzzy logic’ (University Science Press, An Imprint of Laxmi Publications Pvt. Ltd., 2010. 2010)
\\\\
13	Limsetto, N., and Waiyamai, K.: ‘Handling Concept Drift via Ensemble and Class Distribution Estimation Technique’, in Editor (Ed.)\^(Eds.): ‘Book Handling Concept Drift via Ensemble and Class Distribution Estimation Technique’ (Springer Berlin Heidelberg, 2011, edn.), pp. 13-26
\\\\
14	Lu, Y., Cheung, Y.M., and Tang, Y.Y.: ‘Hybrid sampling with bagging for class imbalance learning’, in Editor (Ed.)\^(Eds.): ‘Book Hybrid sampling with bagging for class imbalance learning’ (Springer Verlag, 2016, edn.), pp. 14-26
\\\\
15	Merikangas, A., Mendola, P., Pastor, P., Reuben, C., and Cleary, S.: ‘The association between major depressive disorder and obesity in US adolescents: results from the 2001–2004 National Health and Nutrition Examination Survey’, Journal of Behavioral Medicine, 2012, 35, (2), pp. 149-154
\\\\
16	Mowery, D., Smith, H., Cheney, T., Stoddard, G., Coppersmith, G., Bryan, C., and Conway, M.: ‘Understanding Depressive Symptoms and Psychosocial Stressors on Twitter: A Corpus-Based Study’, Journal of Medical Internet Research, 2017, 19, (2)
\\\\
17	Nguyen, B., Weiss, P., Beydoun, H., and Kancherla, V.: ‘Association between blood folate concentrations and depression in reproductive aged U.S. women, NHANES (2011–2012)’, Journal of Affective Disorders, 2017, 223, pp. 209-217
\\\\
18	Ophir, Y., Asterhan, C.S.C., and Schwarz, B.B.: ‘Unfolding the notes from the walls: Adolescents’ depression manifestations on Facebook’, Computers in Human Behavior, 2017, 72, pp. 96-107
\\\\
19	Ostir, G.V., Berges, I.M., Ottenbacher, A., and Ottenbacher, K.J.: ‘Patterns of change in depression after stroke’, J Am Geriatr Soc, 2011, 59, (2), pp. 314-320
\\\\
20	Peng, Z., Hu, Q., and Dang, J.: ‘Multi-kernel SVM based depression recognition using social media data’, International Journal of Machine Learning and Cybernetics, 2017
\\\\
21	Reece, A.G., and Danforth, C.M.: ‘Instagram photos reveal predictive markers of depression’, EPJ Data Science, 2017, 6, (1), pp. 15
\\\\
22	Rokach, L.: ‘Ensemble-based classifiers’, Artificial Intelligence Review, 2010, 33, (1), pp. 1-39
\\\\
